Research Report: Longitudinal models of human mobility

### 2017-11-07 thesisReport.Rmd
added a few details

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggthemes)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggthemes)
library(ggplot2)
```

@@

*An asside as to my conversation with Peter on 07.11*

We can get some trackers on people to measure movement constantly and be a "golden standard" to evaluate the models.

For December, it would be nice to have the Lit Rev section, plus an exploration of the problem.
